%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

\newcommand\cpp{C\raisebox{0.5ex}{\tiny\textbf{++}}}

 \renewcommand*{\labelitemi}{\strut\textcolor{color1}{\large\rmfamily\textbullet}}
% adjust the page margins
\usepackage[top=.3in, bottom=.3in, left=.4in, right=.5in]{geometry}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Daniel}{Loman}
%\address{726 De La Vina}{Santa Barbara Ca 93101}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[fixed]{(805) 901-8781}
\email{loman.daniel@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.DanLoman.org}                         % optional, remove / comment the line if not wanted
\social[github]{http://github.com/dloman}                              % optional, remove / comment the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
\section{Work Experience}
\cventry{2012--Present}{Software Developer - Analyst}{Toyon Research Corp}{Goleta, CA}{}{
  \begin{itemize}
    \item Designed, implemented and maintain framework for enabling cross platform native and web
      rapid application development across multiple divisions and projects.
    \item Lead architect and developer of a GPS denied indoor visual inertial odometry sensor data fusion application written in \cpp17 and react.
      Led development of both firmware, software, integration testing, HIL testing, field tests and demonstrations.
    \item Started and ran an internal \cpp \hspace{.4mm} user-group/meet-up to improving younger developers skills and to
      facilitate knowledge transfer. This format has been adopted internally across several disciplines.
    \item Implemented hardware accelerated image processing pipeline for real-time SLAM applications.
    \item Lead architect and developer of a distributed multi-agent UAS mission planning and control application.
      Flight tested on over 11 different fielded government UAS platforms.
    \item Lead developer of an experimental distributed multi-threaded sensor resource management application
            and an event based tactical air radar simulation written in \cpp11 and wxWidgets.
    \item Developed and maintained H264 video and telemetry encoding, decoding infrastructure.
    \item Train and supervise software team consisting of full time developers as well as interns.
  \end{itemize}
}

\cventry{2011--2012}{Engineering Intern}{Aerius Photonics LLC}{Ventura, CA}{}{
  \begin{itemize}
	\item Experimented with vertical cavity lasers and performed necessary data analysis using
    SciPy, NumPy, Matplotlib, and pandas.
    \item Manufactured, calibrated, and tested laser range finders, proximity sensors, and altimeters.
    \item Designed, built, and tested custom circuit boards using Altium for the R\&D of
		new prototype lasers.
  \end{itemize}
}

\cventry{2010--2011}{Undergraduate Researcher}{Compact Muon Solenoid Group LHC UCSB}{Goleta, CA}{}{
  \begin{itemize}
    \item Performed analysis and manipulation of 100Gb+ sets.
    \item Implemented, tested, and analyzed the performance of a neural network intended to improve the signal
		to noise ratio in single and double lepton collisions pertinent to the search for the Higgs boson.
  \end{itemize}
}

\cventry{2006}{Engineering Intern}{Surface Targets Naval Airwarfare Center DOD}{Port Hueneme, CA}{}{
  \begin{itemize}
    \item Built and tested remote controlled Jet-Skis used for target practice by the Navy.
    \item Assisted in the building and maintenance of larger remote controlled surface targets.
    \item Designed and machined custom parts for the manufacture of remote controlled surface targets.
  \end{itemize}
}

\cventry{2005--2006}{Engineering Intern}{Phoenix MotorCars Inc.}{Ojai, CA}{}{
  \begin{itemize}
    \item Built and tested the battery pack for a prototype electric taxi cab startup.
  \end{itemize}
}

\vspace{-1mm}
\section{Education}
\cventry{2012}{Computational Science}{San Diego State University}{San Diego, CA}{}{}  % arguments 3 to 6 can be left empty
\cventry{2009--2011}{BS, Physics}{University of California Santa Barbara}{Santa Barbara, CA}{}{}  % arguments 3 to 6 can be left empty

\vspace{-1mm}

\section{Technical Experience}
\cvline{\textbf{Languages}}{ \cpp, JavaScript, Dart, Flutter, C, Python, Matlab, Java, MPI, CUDA, OpenMP}
\cvline{\textbf{Skills}}{Computer Vision, Distributed Systems, Sensor Data Fusion, Data Driven Design, TDD, VR, AR}
\cvline{\textbf{Technologies}}{asio, boost, yocto, websockets, Unreal Engine, nodejs, react, bootstrap, ffmpeg, Video Encoding/Decoding, Android, Numpy, pandas, Scipy, wxWidgets, QT, Git, Vim, Gdb, Valgrind, MISB, \LaTeX, Linux, Windows, OSX}

\section{Personal Projects and Experience}
\cventry{}{}{}{}{}{
\vspace{-8mm}
  \begin{itemize}
    \item Winner in the Most Followed category of the
\href{http://hackaday.io/project/548-Sonic-Screw-Driver-Door-Lock}{\textcolor{color2}{\textbf{Hackaday Sci-Fi Contest}}}
    \item Built physical version of the mobile game Space Team which was displayed at the Moxi Museum
    \item Details for these and additional electronics/software projects available at Project Blog and Github Profile
		\item Volunteer water polo coach at UCSB.
    \item Member of the board of directors of the Santa Barbara Hackerspace and the Los Angeles Contemporary Archive.
    \item Further details available at \href{http://danloman.org}{\textcolor{color2}{\textbf{danloman.org}}} and \href{http://github.com/dloman}{\textcolor{color2}{\textbf{github.com/dloman}}}
  \end{itemize}
}

\end{document}


%% end of file `template.tex'.
